---
title: "Compilation Report | Corpus of Resolutions: UN Security Council"
author: Seán Fobbe
geometry: margin=3cm
fontsize: 11pt
papersize: a4
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    pandoc_args: --listings
    includes:
      in_header: tex/Preamble_EN.tex
      before_body: [temp/Definitions.tex, tex/Titlepage_Compilation.tex]
bibliography: temp/packages.bib
nocite: '@*'
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = TRUE,
                      message = TRUE,
                      collapse = TRUE,
                      comment = "#>")
```


```{r, results = "asis", echo = FALSE}
cat(readLines("README.md"),
    sep = "\n")
```


# Load Packages


```{r}

library(targets)
library(tarchetypes)
library(RcppTOML)
library(future)
library(data.table)
library(quanteda)
library(knitr)
library(kableExtra)
library(igraph)
library(ggraph)

tar_unscript()
```


# Preamble

## Definitions

```{r}

## Datestamp
datestamp <- Sys.Date()
print(datestamp)

## Date and Time (Begin)
begin.script <- Sys.time()

## Read Configuration
config <- RcppTOML::parseTOML("config.toml")
print(config)


# Define Analysis Folder
dir.analysis <- paste0(getwd(),
                       "/analysis")


```



## Create Folders


```{r}

dirs <- c("output",
          "temp")

dir.create(dir.analysis, showWarnings = FALSE)

lapply(dirs, dir.create, showWarnings = FALSE)

```





## Write Package Citations

```{r}
knitr::write_bib(renv::dependencies()$Package,
                 "temp/packages.bib")
```



# Global Variables


## Define Packages

```{targets global-packages, tar_globals = TRUE}

tar_option_set(packages = c("tarchetypes",  # Additional targets functions
                            "RcppTOML",     # Read and write TOML files
                            "zip",          # Enhanced ZIP handling
							"testthat",     # Unit tests
							"rvest",        # Web Scraping
                            "knitr",        # Scientific reporting
                            "kableExtra",   # Enhanced kable tables
                            "ggplot2",      # Advanced data vizualization
							"ggraph",       # Graph visualization
                            "scales",       # Scaling of figures
                            "viridis",      # Viridis palette
                            "RColorBrewer", # ColorBrewer palett
							"pdftools",     # Extract PDF files
							"readtext",     # Read TXT files
                            "quanteda",     # Advanced computer linguistics
                            "quanteda.textstats", # Text statistics
                            "quanteda.textplots", # Text visualizations
                            "future",       # Parellel computing
                            "future.apply", # Higher-order functions for future
                            "data.table"    # Advanced tabular data processing
                            )
               )


tar_option_set(workspace_on_error = TRUE) # Save Workspace on Error
tar_option_set(format = "qs")

```



## Configuration


```{targets global-config, tar_globals = TRUE}

datestamp <- Sys.Date()

config <- RcppTOML::parseTOML("config.toml")


dir.analysis <- paste0(getwd(),
                       "/analysis")

## Caption for diagrams
caption <- paste("Fobbe/Ridi/Gasbarri | DOI:",
                 config$doi$data$version)


## Prefix for figure titles
prefix.figuretitle <- paste(config$project$shortname,
                            "| Version",
                            datestamp)

## File prefix
prefix.files <- paste0(config$project$shortname,
                       "_",
                       datestamp)


if (config$cores$max == TRUE){
    fullCores <- parallel::detectCores()
}


if (config$cores$max == FALSE){
    fullCores <- as.integer(config$cores$number)
}

```



## Define Functions

```{targets global-functions, tar_globals = TRUE}

lapply(list.files("functions", pattern = "\\.R$", full.names = TRUE), source)

```



## Define Metadata for TXT Files

```{targets global-txtvars, tar_globals = TRUE}

docvarnames <- c("body",
                 "doctype",
                 "res_no",
                 "year",
                 "language")

```




## Define Source Files

```{targets global-sourcefiles, tar_globals = TRUE}

files.source.raw <-  c(list.files(pattern = "\\.R$|\\.toml$|\\.md$|\\.Rmd$"),
					   "reports",
                       "data",
                       "functions",
                       "tex",
                       "gpg",
                       "buttons",
                       list.files(pattern = "renv\\.lock|\\.Rprofile",
                                  all.files = TRUE),
                       list.files("renv",
                                  pattern = "activate\\.R",
                                  full.names = TRUE))

```

# Pipeline: Construction




## File Read Targets

Defines targets that track and read input data files. Source files are not read into R, but tracked to serve as a trigger for rebuilding the relevant ZIP archive.



### Source Code

```{targets tar.file1}
tar_target(files.source,
           files.source.raw,
           format = "file")

```


### Changelog

```{targets tar.file2}
tar_target(changelog,
           "CHANGELOG.md",
           format = "file")
```



### Read Table of Record Pages (Stable)



```{targets tar.file3}
list(
    tar_target(record.table.file,
               "data/UNSC_Record-Table_2636.csv",
               format = "file"),
    tar_target(record.table.stable,
               fread(record.table.file))
)
```


## Download



### Build Table of Record Pages (Final)


```{targets tar.download.recordtable}
tar_target(dt.record.final,
           f.record_table(recordtable.stable = record.table.stable,
                                 limit = 2640,
								 debug.toggle = config$debug$toggle,
								 debug.sample = config$debug$sample))
```




### Download HTML Records for Resolutions



```{targets tar.download.records.res}
tar_target(files.record.res,
                f.download(url = dt.record.final$url_record,
                           filename = paste0(dt.record.final$res_no, ".html"),
                           dir = "record_resolution",
                           sleep.min = 0.5,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```






### Parse Resolution HTML Records

```{targets tar.download.parse.res}
tar_target(dt.download,
           f.parse_records_full(files.record.res))
		   
```





### Download HTML Records for Drafts



```{targets tar.download.records.draft}
tar_target(files.record.draft,
                f.download(url = dt.download$url_record_draft,
                           filename = paste0(dt.download$res_no, ".html"),
                           dir = "record_draft",
                           sleep.min = 0.5,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 5,
                           retry.sleep.max = 10,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```



### Download HTML Records for Meeting Records



```{targets tar.download.records.meeting}
tar_target(files.record.meeting,
                f.download(url = dt.download$url_record_meeting,
                           filename = paste0(dt.download$res_no, ".html"),
                           dir = "record_meeting",
                           sleep.min = 1,
                           sleep.max = 1.5,
                           retries = 3,
                           retry.sleep.min = 5,
                           retry.sleep.max = 10,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```




### Parse Draft HTML Records

```{targets tar.download.parse.draft}
tar_target(url.draft,
           f.parse_records_url(files.record.draft,
                               prefix = "url_draft_"))

```




### Parse Meeting HTML Records

```{targets tar.download.parse.meeting}
tar_target(url.meeting,
           f.parse_records_url(files.record.meeting,
                               prefix = "url_meeting_"))
		   
```



### Finalize Download Table

```{targets tar.download.table.final}
tar_target(dt.download.final,
           f.download_table_finalize(dt.download = dt.download,
                                     dt.record = dt.record.final,
                                     url.meeting = url.meeting,
                                     url.draft = url.draft))


```



### Download Resolutions


#### Arabic

```{targets tar.download.res.ar}
tar_target(files.res.pdf.ar,
                f.download(url = dt.download.final$url_res_ar,
                           filename = paste0(dt.download.final$doc_id, "_AR.pdf"),
                           dir = "pdf_res_ar",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```



#### Chinese

```{targets tar.download.res.zh}
tar_target(files.res.pdf.zh,
                f.download(url = dt.download.final$url_res_zh,
                           filename = paste0(dt.download.final$doc_id, "_ZH.pdf"),
                           dir = "pdf_res_zh",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```



#### English

```{targets tar.download.res.en}
tar_target(files.res.pdf.en,
                f.download(url = dt.download.final$url_res_en,
                           filename = paste0(dt.download.final$doc_id, "_EN.pdf"),
                           dir = "pdf_res_en",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```


#### French

```{targets tar.download.res.fr}
tar_target(files.res.pdf.fr,
                f.download(url = dt.download.final$url_res_fr,
                           filename = paste0(dt.download.final$doc_id, "_FR.pdf"),
                           dir = "pdf_res_fr",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```




#### Russian

```{targets tar.download.res.ru}
tar_target(files.res.pdf.ru,
                f.download(url = dt.download.final$url_res_ru,
                           filename = paste0(dt.download.final$doc_id, "_RU.pdf"),
                           dir = "pdf_res_ru",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```


#### Spanish


```{targets tar.download.res.es}
tar_target(files.res.pdf.es,
                f.download(url = dt.download.final$url_res_es,
                           filename = paste0(dt.download.final$doc_id, "_ES.pdf"),
                           dir = "pdf_res_es",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```





### Download Drafts

```{targets tar.download.draft.en}
tar_target(files.draft.pdf.en,
                f.download(url = dt.download.final$url_draft_en,
                           filename = paste0(dt.download.final$doc_id, "_Draft_EN.pdf"),
                           dir = "pdf_draft_en",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```



### Download Meeting Records

```{targets tar.download.meeting.en}
tar_target(files.meeting.pdf.en,
                f.download(url = dt.download.final$url_meeting_en,
                           filename = paste0(dt.download.final$doc_id, "_MeetingRec_EN.pdf"),
                           dir = "pdf_meeting_en",
                           sleep.min = 0.3,
                           sleep.max = 1,
                           retries = 3,
                           retry.sleep.min = 2,
                           retry.sleep.max = 5,
                           timeout = config$download$timeout,
                           debug.toggle = FALSE),
                format = "file")

```



## Convert Targets



### Convert to TXT and ingest into R


```{targets tar.convert1}

list(tar_target(files.res.txt.en,
                f.tar_pdf_extract(x = files.res.pdf.en,
                                  outputdir = "txt.res.en",
								  multicore = config$parallel$extractPDF,
                                  cores = fullCores),
                format = "file"),
     tar_target(dt.txt.en,
                f.readtext(x = files.res.txt.en,
                           docvarnames = docvarnames))
     )

```





## Report Targets


### Write \LaTeX Definitions


```{targets tar.report1}
tar_target(latexdefs,
           f.latexdefs(config,
                       dir = "temp",
                       version = datestamp),
	       format = "file")

```





## Write Targets









## ZIP Targets


### Create ZIP: Source Code


```{targets tar.zip1}
tar_target(zip.source,
           f.tar_zip(files.source,
                     filename = paste0(prefix.files,
                                       "_Source_Code.zip"),
                     dir = "output",
                     mode = "mirror"),
           format = "file")
```
	

### Create ZIP: PDF Original


```{targets tar.zip.pdf.original}
tar_target(zip.pdf.original,
           f.tar_zip(c(files.res.pdf.ar,
                       files.res.pdf.en,
                       files.res.pdf.es,
                       files.res.pdf.fr,
                       files.res.pdf.ru,
                       files.res.pdf.zh),
                     filename = paste0(prefix.files,
                                       "_Resolutions_PDF.zip"),
                     dir = "output",
                     mode = "mirror"),
           format = "file")
```





# Pipeline: Compilation



## Run Pipeline

```{r pipeline-run, results = "hide"}
tar_make()
```



## Visualization

```{r, pipeline-graph, width = 9, height = 9}

edgelist <- tar_network(targets_only = TRUE)$edges
setDT(edgelist)

g  <- igraph::graph.data.frame(edgelist,
                               directed = TRUE)


ggraph(g,
       'dh') + 
    geom_edge_diagonal(colour = "grey")+
    geom_node_point()+
    geom_node_text(aes(label = name),
                   size = 2,
                   repel = TRUE)+
    theme_void()

```
                       




# Pipeline: Analysis


## Full List



```{r, pipeline-list}

meta <- tar_meta(fields = c("type", "bytes"), complete_only = TRUE)
setDT(meta)
meta$MB <- round(meta$bytes / 1e6, digits = 2)

kable(meta[order(type, name)],
      format = "latex",
      align = "r",
      booktabs = TRUE,
      longtable = TRUE) %>% kable_styling(latex_options = "repeat_header")


```

\newpage
## Timing


```{r, pipeline-timing}

meta <- tar_meta(fields = c("time", "seconds"), complete_only = TRUE)
setDT(meta)

kable(meta[order(-seconds)],
      format = "latex",
      align = "r",
      booktabs = TRUE,
      longtable = TRUE) %>% kable_styling(latex_options = "repeat_header")


```

## Duration

```{r, pipeline-runtime}
runtime.sum <- sum(meta$seconds)

## Seconds
print(runtime.sum)

## Minutes
runtime.sum / 60

## Hours
runtime.sum / 3600
```



\newpage
## Warnings


```{r, pipeling-warnings}

meta <- tar_meta(fields = "warnings", complete_only = TRUE)
setDT(meta)

kable(meta,
      format = "latex",
      align = "r",
      booktabs = TRUE,
      longtable = TRUE) %>% kable_styling(latex_options = "repeat_header")


```



## Errors

```{r, pipeline-errors}

meta <- tar_meta(fields = "error", complete_only = TRUE)
setDT(meta)

kable(meta,
      format = "latex",
      align = "r",
      booktabs = TRUE,
      longtable = TRUE) %>% kable_styling(latex_options = "repeat_header")


```












# Finalize

```{r}

## Date Stamp
print(datestamp) 

## Date and Time (Begin)
print(begin.script)


## Date and Time (End)
end.script <- Sys.time()
print(end.script)


## Runtime for Script
print(end.script - begin.script)

```


# Parameters for Strict Replications


```{r}
system2("openssl", "version", stdout = TRUE)

sessionInfo()

```


# Bibliography
