---
title: "Codebook | Corpus of Resolutions: UN Security Council"
author: "Seán Fobbe, Lorenzo Gasbarri and Niccoló Ridi"
geometry: margin=3cm
papersize: a4
fontsize: 11pt
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    pandoc_args: --listings
    includes:
      in_header: ../tex/Preamble_EN.tex
      before_body: [../temp/Definitions.tex, ../tex/Titlepage_Codebook.tex]
bibliography: ../temp/packages.bib
nocite: '@*'
---




```{r, setup, include=FALSE}
knitr::opts_chunk$set(fig.path = file.path("..", "analysis/"),
                      dev = config$fig$format,
                      dpi = config$fig$dpi,
                      fig.align = config$fig$align,
                      echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

```


```{r, echo = FALSE}
tar_load(latexdefs)
tar_load(dt.var_codebook)
tar_load(var_lingstats)
tar_load(lingstats.summary)
tar_load(dt.final)
tar_load(igraph_citations)


```



# Introduction

The **United Nations Security Council (UNSC)** is the most influential of the principal UN organs. Composed of five permanent and ten non-permanent members, its functioning is constrained by the political context in which it operates. During the Cold War, the complex political relationships between the permanent members and their veto powers significantly affected the capacity of the UNSC to address violations of international peace and security, with only 646 resolutions passed from 1946 to 1989. 

Since the 1990s, the activity of the UN Security Council has increased dramatically and produced 2721 resolutions up to the end of 2023. The length, complexity and thematic breadth of the resolutions has also increased, prompting calls to redefine it as a quasi-legislative body.

Under Articles 24 and 25 of the UN Charter, member states have conferred upon the UNSC the \enquote{primary responsibility for the maintenance of international peace and security} and have agreed \enquote{to accept and carry out} its decisions. The discharge of this function is carried out through the powers bestowed upon it under Chapter VI of the UN Charter, \enquote{Pacific Settlement of Disputes}, Chapter VII, \enquote{Action with Respect to Threats to the Peace, Breaches of the Peace, and Acts of Aggression}, Chapter VIII, \enquote{Regional Arrangements}, and Chapter XII, \enquote{International Trusteeship System}. 

Under the peace and security mandate, its areas of activity cover disarmament, pacific settlement of disputes, enforcement, and, until 1994, strategic areas in a trusteeship agreement. Its functions also pertain to the correct working of the United Nations, covering issues of membership, the appointment of the Secretary General, the elections of judges of the International Court of Justice (ICJ), the calling of special and emergency sessions of the General Assembly, the amendment of the Charter and of the ICJ Statute.

The **Corpus of Resolution: UN Security Council (CR-UNSC)** collects and presents for the first time all resolutions, drafts, and meeting records of the UN Security Council with their associated metadata, as published by the UN Digital Library.\footnote{\url{https://digitallibrary.un.org/}.}

The quantitative analysis of international legal data is still in its infancy, a situation exacerbated by the lack of high-quality empirical data. Most advanced data sets are held in commercial databases and are therefore not easily available to academic researchers, journalists and the general public. With this data set we hope to contribute to a more systematic and empirical view of the international legal system. In an international community founded on the rule of law the activities of the United Nations must be public, transparent and defensible. In the 21st century this requires quantitative scientific review of decisions and actions. 
 
Design, construction and compilation of this data set are based on the principles of general availability through freedom from copyright (public domain status), strict transparency and full scientific reproducibility. The *FAIR Guiding Principles for Scientific Data Management and Stewardship* (Findable, Accessible, Interoperable and Reusable) inspire both the design and the manner of publication.\footnote{Wilkinson, M., Dumontier, M., Aalbersberg, I. et al. The FAIR Guiding Principles for Scientific Data Management and Stewardship. Sci Data 3, 160018 (2016). <\url{https://doi.org/10.1038/sdata.2016.18}>.}




# Reading Files

The data are published in open, interoperable and widely used formats (CSV, TXT, PDF, GraphML). They can be used with all modern programming languages (e.g. Python or R) and graphical interfaces. The PDF collections are intended to facilitate traditional legal research.

**Important:** Missing values are always coded as \enquote{NA}.


## CSV Files

 Working with the CSV files is recommended. CSV\footnote{The CSV format is defined in RFC 4180: <\url{https://tools.ietf.org/html/rfc4180}>.} is an open and simple machine-readable tabular data format. In this data set values are separated by commas. Each column is a variable and each row is a document. Variables are explained in detail in section \ref{variables}.


To read \textbf{CSV} files into R we strongly recommend using the fast file reader **fread()** from the **data.table** package (available on CRAN). The file can be read into \textbf{R} like so: 

```{r, eval = FALSE, echo = TRUE}
library(data.table)

unsc <- fread("CR-UNSC_2023-08-23_EN_CSV_Main-Dataset.csv")
```



## TXT Files

The \textbf{TXT} files, including metadata, can be read into \textbf{R} with the package \textbf{readtext} (available on CRAN):

```{r, eval = FALSE, echo = TRUE}
library(readtext)

unsc <- readtext("txt_res_en/*.txt",
                 docvarsfrom = "filenames", 
                 docvarnames = c("body",
                                 "doctype",
                                 "res_no",
                                 "year",
                                 "language"),
                 dvsep = "_", 
                 encoding = "UTF-8")

```






# Data Set Design


## Overview

The \textbf{\datatitle\ (\datashort)} collects and structures in human- and machine-readable form all published resolutions of the United Nations Security Council (UNSC) in all six official UN languages (Arabic, Chinese, English, French, Spanish and Russian). Specialized variants of the data set provide citation data and a bibliopgrahic database compatible with a wide range of end-user applications.

This structure and content of this section build on the suggestions offered in: Gebru, T., Morgenstern, J., Vecchione, B., Vaughan, J. W., Wallach, H., Iii, H. D., & Crawford, K. (2021). Datasheets for datasets. Communications of the ACM, 64(12), 86-92.


## Table of Sources


\begin{centering}
\begin{longtable}{P{5cm}p{9cm}}

\toprule
 Data Source & Citation \\

\midrule

 Primary Data Source & \url{https://digitallibrary.un.org/}\\
 Source Code & \url{\softwareversionurldoi}\\

\bottomrule

\end{longtable}
\end{centering}



## Motivation

Our motivation in creating this dataset is to enhance international legal and political research in general, increase understanding of the work of the \unsc\ and facilitate creative digital work in the area of international peace and security. 

The \datashort\ is a general-purpose dataset  intended to provide high-quality legal and political data that enables researchers, practitioners, civil society, UN officials, governments and any other interested parties to address a wide range research questions related to the \unsc .

The use of the main data set is not limited to a particular line of inquiry or specific discipline. Specialized variants of the data set offer citation data and a bibliographic database compatible with a wide range of end-user applications.


## Funding

The authors did not receive any specific funding to work on this dataset. All work on the dataset was carried out in addition to their regular academic activities. 



## Composition

The dataset is primarily composed of the texts of all resolutions in all official UN languages published by the \unsc . We aim for a complete accounting of all resolutions, up to the most recent resolution that was available through the UN Digital Library on the date of data set creation. We further provide the English texts of the draft resolutions and meeting records associated with each resolutons. 

Each resolution is accompanied by as much high-quality metadata as could be acquired and validated, as well as additional metadata extracted from the text of the resolutions. The exact composition and scope of the data set is documented and visualized with frequency tables at the end of this Codebook.

The data set is self-contained, but it contains the original URLs to UN Digital Library record pages and URLs to individual PDF files for purposes of reproducibility, data validation and creating digital applications that would benefit from integrating linked open data. We assume these URLs will remain stable over time, but their maintenance depends on the actions of the UN Digital Library. In case of link failure, newer version of the data set will contain updated links.

There are no recommended data splits. However, all resolutions are consecutively numbered and timestamped with the date of adoption. Time series analyses should take this into account.




## Sensitive Data

Resolutions of the \unsc\ are publicly available official documents of an international organization. The metadata strictly relates to these public documents. While the text of the resolutions contains references to individuals and organizations, this information has always been published in unredacted form by the \unsc . We have not redacted any of this information to ensure the integrity of these official documents. In any case, the maintenance of international peace and security at the highest international level is a public affair of such magnitude that privacy rights of individuals and organizations cannot prevent their mention and discussion of their activities in official texts of the \unsc .




##  Data Collection

Data were collected with the explicit consent of the United Nations. All documents were downloaded via TLS-encrypted connections and cryptographically signed after data processing was complete. The data set collects all resolutions issued by the \unsc\ that were published by the UN Digital Library up to resolution number `r max(dt.final$res_no)`.

  


```{r, CR-UNSC_Workflow_blackwhite, fig.width = 16, fig.height = 18, fig.pos = "p", fig.cap = "Dataset Compilation Process"}


edgelist <- tar_network(targets_only = TRUE)$edges
setDT(edgelist)

g  <- igraph::graph.data.frame(edgelist,
                               directed = TRUE)


ggraph(g,
       'sugiyama') + 
    geom_edge_diagonal(colour = "grey70")+
    geom_node_point(size = 2)+
    geom_node_text(aes(label = name),
                   size = 2,
                   repel = TRUE)+
    theme_void()+
    labs(
        title = paste(prefix.figuretitle,
                      "| Data set compilation process"),
        caption = caption
    )+
    theme(
        plot.title = element_text(size = 14,
                                  face = "bold"),
        plot.margin = margin(10, 20, 10, 10)
    )

```


## Processing and Quality Assurance

Dozens of automated tests were conducted to ensure the quality of the data and metadata. These include:

- Validation of variable types
- Plausibility checks on expected values for many variables (e.g. minima, maxima, plausible values)
- Completeness checks on download and full dataset
- Text quality and language purity checks
- Creation of visualizations for many common descriptive analyses

For results of each test and more information on the construction of the data set please refer to the Compilation Report and the Quality Assurance Report.

The raw data for all stages of the data pipeline (\enquote{targets}) was stored and is published together with the source code. The original files acquired from the UN Digital Library are part of the dataset itself, insofar as we consider them useful to other users. 




## Uses

The dataset has been designed to be useful for any and all purposes related to the quantitative analysis of international law and to traditional researchers who seek a complete collection of \unsc resolutions. The dataset is identified by a unique Digital Object Identifier (DOI) and, if correctly cited, all public applications should be searchable on the internet.

The dataset can potentially be used in the following applications

- Information retrieval (discovery of relevant and related resolutions)
- Automatic summarization (full text and brief summaries and titles available)
- Topic analysis (full-text available)
- Citation analysis (UNSC and UNGA citation data is included)
- Machine translation (all six UN languages available, but note quality and completeness constraints on non-English texts)
- Argument mining

The dataset should not be used for the following tasks:

- Prediction of adoption success or voting behavior (dependent variable) based on the text of a resolution or draft (input variable). The data set contains only successfully adopted resolutions, so there is no control group of unsuccessful drafts.


## Distribution

The datast is cleared for immediate use by the general public and professional audiences. It is distributed free of charge. 

Authentic copies of the data set and source code will be distributed on the internet via Zenodo, a non-profit scientific repository managed by CERN. 

The concept of the data set is uniquely identified by a digital object identififer (DOI), which always resolves to the latest version. In addition to the \enquote{Concept DOI} each version of the data set is further uniquely identified with its own DOI, the \enquote{Version DOI}.

The dataset and source code are distributed under standardized and widely recognized open licenses. We are not aware of any regulatory restrictions that would limit distribution or re-distribution of the dataset.

Development versions of the source code are available on GitHub but carry no promise or expectation of correctness or functionality.


## Copyright Status: Public Domain

The copyright status of UN documents, resolutions, drafts and meeting records is governed by UN Administrative Instruction ST/AI/189/Add.9/Rev.2 of 17 September 1987.\footnote{\url{https://en.wikisource.org/wiki/Administrative_Instruction_ST/AI/189/Add.9/Rev.2}} UN Administrative Instruction ST/AI/189/Add.9/Rev.2/Add.2 extended the temporal scope of the former until \enquote{further revision to that instruction}.\footnote{\url{https://en.wikisource.org/wiki/Administrative_Instruction_ST/AI/189/Add.9/Rev.2/Add.2}} As no revision has been published to this day, the rules remain in force. The most recent Index to Administrative Issuances ST/IC/2019/1 lists Administrative Instruction ST/AI/189/Add.9/Rev.2 as active.

UN Administrative Instruction ST/AI/189/Add.9/Rev.2 of 17 September 1987 clearly states:

> 2. The following categories of material will, as at present, be left in the public domain, i.e., the United Nations will not seek copyright therefor unless, prior to issue and in exceptional circumstances, the Publications Board decides otherwise, in consultation with the Office of Legal Affairs.
>
> > (a) Official Records: a series of printed publications relating to the proceedings of organs or conferences of the United Nations. They include verbatim or summary records, documents or check-lists of documents, issued in the form of annexes to those records, including periodic supplements, such as the quarterly ones of the Security Council; and reports to those organs of their subordinate or affiliated bodies, compilations of resolutions, certain reports of the Secretary-General and other selected publications, which are issued in the form of supplements;
> > (b) United Nations documents: written material officially issued under a United Nations document symbol, regardless of the form of production, although, in practice, the term is applied mainly to material offset from typescript and issued under a masthead. The term also applies to written material issued simultaneously or sequentially in the form of documents and publications;


We wish to honor the letter and spirit of this UN policy. To ensure the widest possible distribution of official UN documents and to promote the international rule of law we waive any copyright that might have accrued by creating the dataset under a \textbf{Creative Commons CC0 1.0 Universal (CC0 1.0) Public Domain Dedication}. 

For details of the waiver please refer to the CC0 copyright notice at the beginning of this Codebook or visit the Creative Commons website for the full terms.\footnote{\url{https://creativecommons.org/publicdomain/zero/1.0/legalcode}}




## Maintenance and Updates

Authentic versions of the dataset and source are always published and hosted on Zenodo.\footnote{\url{https://www.zenodo.org}} Zenodo guarantees the professional storage of published records in CERN's Data Centre and public availability for the lifetime of CERN, which has a defined research program for at least 20 years.

Maintenance and further development of the dataset and source code will be carried out by the author(s) for the foreseeable future. Contact details are available on the Zenodo page of the data set.

We intend to update the dataset at least once per year. All updates will be published on Zenodo and uniquely identified by date stamps and Version DOIs. Older versions will continue to be available on Zenodo under their original Version DOI.

Contributions to the dataset can be made by reporting issues and suggesting enhancements to the authors, as well as proposing code changes and additions on GitHub.




## Source Code and Compilation Report

The full Source Code for the creation of this data set, the resulting Compilation Report, a Quality Assurance Report and this Codebook are published open access and permanently archived with Zenodo, the scientific repository of CERN.

With every compilation of the full data set an extensive **Compilation Report** is created in a professionally layouted PDF format. The Compilation Report includes the full data pipeline, comments and explanations of design decisions, relevant computational results, exact timestamps and a table of contents with clickable internal hyperlinks to each section. The Compilation Report is published under the same DOI as the Source Code.

For details of the construction and validation of the data set please refer to the Compilation Report and Quality Assurance Report in addition to this Codebook.



## Limitations

Users should bear in mind certain important limitations:

- The data set contains only those documents which were published by the \unsc\ and have been made available by the UN Digital Library on its official website (\emph{publication bias}). This mainly affects languages other than English
- While Tesseract yields high-quality OCR results, current OCR technology is not perfect and minor errors must be expected (\emph{OCR bias}). This affects resolutions and associated drafts and meeting records up to resolution 899.
- The OCR texts for all languages other than English were *not* manually post-processed, so, in addition to OCR errors, may contain superfluous texts from other documents printed on the same page. This affects resolutions and associated drafts and meeting records up to resolution 899.









# Variants and Target Audiences

## Overview of Variants

The published data set contains all six official UN languages (English, French, Spanish, Arabic, Chinese and Russian) and is published in several different variants intended for specific target audiences. In particular, a tabular CSV variant for general data analysis, a GraphML network representation for citation analysis, a PDF variant for traditional research and a BIBTEX variant to assist with efficient citation of UNSC resolutions.


### Recommended for Quantitative Research

- ALL\_CSV\_FULL 
- ALL\_CSV\_META 
- ALL\_TXT 
- ANALYSIS 
- CITATIONS\_GRAPHML 

### Recommended for Traditional Research

- ALL\_PDF\_RESOLUTIONS 
- ALL\_TXT 
- ANALYSIS 
- BIBTEX\_OSCOLA 
- EN\_PDF\_Drafts 
- EN\_PDF\_Meeting-Records 



## ALL\_CSV\_FULL

A structured tabular representation of the full data set, stored within a single comma-delimited file (CSV). Includes the full texts of resolutions in all languages, draft texts in English, meeting records in English and the full complement of metadata described in the Codebook. 


## ALL\_CSV\_META

A structured tabular representation of the full metadata, contained within a single comma-delimited file (CSV). The *META* CSV variant is equivalent to the *FULL* CSV variant, except that all text variables have been removed. This is particularly useful where disk space is limited or where an analysis requires only metadata.



## ALL\_PDF\_Resolutions

All resolutions issued by the UNSC in all six official UN languages in PDF format as published by the UN Digital Library. Includes resolutions 1 through 899 in English with a new and enhanced OCR text layer created with an advanced LSTM neural network machine learning engine.

OCR versions of other languages are not included in this PDF archive to keep file size reasonable. However, the data pipeline produces PDF files with enhanced OCR text for all languages.

Please note that the gold-standard text for the English versions of resolutions 1 through 899 is only available in the *TXT* variant, the text layer in the English PDF files is OCR output.


## ALL\_TXT

All resolutions issued by the UNSC in all six official UN languages, as well as English drafts and meeting records, in TXT format. The TXT representation was extracted from the original PDF files with simple text layer extraction and alternatively OCR recognition with Tesseract, an advanced LSTM neural network machine learning engine. This variant also includes the revised gold standard texts for resolutions 1 through 899 in English.

Researchers with slow internet connections or who wish to save disk space should consider the *TXT* variant, as this still provides a reasonable visual approximation of the original documents, but offers the advantage of drastically reduced file size.


## ANALYSIS 

This archive contains almost all of the machine-readable analysis output generated during the data set creation process to facilitate further analysis, in CSV format for tables, PDF and PNG format for diagrams. Minor analysis results are documented only in the Compilation Report and the Quality Assurance Report.


## BIBTEX\_OSCOLA

A selection of variables from the metadata converted to `.bibtex` format compliant with the **bl-oscola** 1.7 standard. This file should be importable in all standard reference managers such as Zotero, EndNote, Citavi and Jabref.

Note that the content of the variables \enquote{title} and \enquote{other\_title} are switched in the BIBTEX variant to make for a better experience in bibliography software. The \enquote{other\_title} variable is more informative, but the main data set tries to respect the UN Digital Library naming convention.


## CITATIONS\_GRAPHML

A graph (network) representation of all citations from UNSC resolutions to other UNSC and UNGA resolutions in GraphML format. The format is widely supported, in particular by GUI software such as Gephi. 

The UNSC resolution nodes are associated with as much metadata as makes sense from a network perspective. The file does not include full texts of resolutions or URLs to PDF files. If you wish to select nodes based on the contents of the full text, please run your analysis on the CSV file, export the resolution numbers and use these to select the appropriate nodes in your network analysis software.


## EN\_PDF\_Drafts

All drafts of resolutions texts in English as published by the UN Digital Library, in PDF format. We only include English draft resolutions, as the draft text is primarily negotiated in English. Enhanced OCR versions of the PDF files are produced by the data pipeline, but not included in the published data set to keep file size reasonable.

Please note that the files are named according to the associated final resolution (and not the official document symbol of the draft) to speed up findability.


## EN\_PDF\_Meeting-Records

All meeting records associated with resolutions in English as published by the UN Digital Library, in PDF format. We only include English draft resolutions, as the draft text is primarily negotiated in English. Enhanced OCR versions of the PDF files are produced by the data pipeline, but not included in the published data set to keep file size reasonable.

Please note that the files are named according to the associated final resolution (and not the official document symbol of the meeting record) to speed up findability.









# Variable Descriptions
\label{variables}

## General Remarks

- Missing values are always coded as \enquote{NA}.
- All Strings are encoded in UTF-8.
- A significant part of the metadata has been drawn from the UN Digital Library metadata records and was originally curated by the UN Digital Library.


## ID Variables

The group ID variables identifies the resolution, its draft, meeting record and various associated documents with symbols and dates.


```{r}

kable(dt.var_codebook[group == "1_id", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```

## Text Variables

Text variables contain the full text of all six language versions of the UN Security Council's resolutions. Also provided are pre-computed statistical measures of the length of each resolution (English text only).


```{r}

kable(dt.var_codebook[group == "2_text", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```

## Thematic Variables

Thematic variables contain a number of different classifications of UN Security Council texts and will prove especially useful for refining the data to fit a thematic research question.


```{r}

kable(dt.var_codebook[group == "3_thematic", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```

## Vote Variables

Vote variables document the voting results and voting patterns of UNSC resolutions. Includes counts, total and disaggregated, as well as individual votes cast by each State. 

Note that the UNSC was enlarged from 11 to 15 members (from 6 to 10 non-permanent members) in 1965, so comparing absolute vote counts is only appropriate before and after those years. All other analyses should use proportions.

When attempting to build prediction models, please bear in mind that the data set only documents successfuly adopted resolutions and their voting data. Many draft resolutions fail during the negotiation stage or because they cannot secure the necessary number of votes. Any prediction model should inclues these failed drafts, but they are not included as part of this dataset.



```{r}

kable(dt.var_codebook[group == "4_vote", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```

## Geographic Variables

Geographic variables provide insight into the geographic distribution of the UNSC's attention. Note that the voting variables contain the geographic distribution of votes.


```{r}

kable(dt.var_codebook[group == "5_geo", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```

## Source Variables

Source variables provide explicit references for the data sources via URLs to UN Digital Library record pages and documents.



```{r}

kable(dt.var_codebook[group == "6_url", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```

\newpage
## Meta Variables

Meta variables provide further information on the data set, including version, DOIs and licensing information. These document provenance and ensure compliance with FAIR Data Principles F1, F3 and R1.1.



```{r}

kable(dt.var_codebook[group == "7_misc", .(varname, type, description)],
      format = "latex",
      align = 'P{3.5cm}P{3cm}p{8cm}',
      booktabs = TRUE,
      longtable = TRUE,
      escape = FALSE,
      col.names = c("Variable",
                    "Type",
                    "Description"))  %>% kable_styling(latex_options = "repeat_header")

```



# Citation Network Data

The CR-UNSC comes with a specialized variant of the dataset that contains all citations from UNSC resolutions to other UNSC resolutions and UNGA resolutions. This graph (network) representation of citations is available in GraphML format.


\ra{1.1}
```{r}

g <- igraph_citations


dt.g <- data.table(Metric = c("Number of Nodes",
                              "Number of Edges",
                              "Mean Degree",
                              "Max Degree",
                              "Min Degree",
                              "Mean In-Degree",
                              "Max In-Degree",
                              "Min In-Degree",
                              "Diameter",
                              "Radius",
                              "Assortativity (Degree)",
                              "Mean Distance"),
                   Value = c(vcount(g),
                                   ecount(g),
                                   mean(degree(g, mode = "all")),
                                   max(degree(g, mode = "all")),
                                   min(degree(g, mode = "all")),
                                   mean(degree(g, mode = "in")),
                                   max(degree(g, mode = "in")),
                                   min(degree(g, mode = "in")),
                                   diameter(g),
                                   radius(g),
                                   assortativity_degree(g),
                                   mean_distance(g)
                                   )
                   )

dt.g.split <- cbind(dt.g[1:6], dt.g[7:12])

kable(dt.g.split,
      digits = 2,
      format.args = list(big.mark = ","),
      format = "latex",
      booktabs = TRUE,
      longtable = TRUE)


```


The UNSC resolution nodes are associated with as much metadata as makes sense from a network perspective. The GraphML file does not include full texts of resolutions. The following meta data variables are included:


```{r}
vertex_attr_names(igraph_citations)
```


If you wish to select nodes based on the contents of the full text, please run your analysis on the CSV file, export the resolution numbers and use these to select the appropriate nodes in your network analysis software.





```{r, CR-UNSC_Citations_Degree, fig.width = 9, fig.height = 6, fig.cap = "Degree distribution of the UNSC citation network."}


g <- igraph_citations
degree.all <- data.table(prop = degree_distribution(g, mode = "all"))
degree.all$degree <- 1:length(degree.all$prop)



ggplot(data = degree.all) +
    geom_bar(aes(x = degree,
                 y = prop),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Degree Distribution of Citations"),
        caption = caption,
        x = "Degree",
        y = "Proportion"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )



```




```{r, CR-UNSC_Citations_In-Degree, fig.width = 9, fig.height = 6, fig.cap = "In-Degree distribution of the UNSC citation network."}


g <- igraph_citations
degree.in <- data.table(prop = degree_distribution(g, mode = "in"))
degree.in$degree <- 1:length(degree.in$prop)



ggplot(data = degree.in) +
    geom_bar(aes(x = degree,
                 y = prop),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| In-Degree Distribution of Citations"),
        caption = caption,
        x = "Degree",
        y = "Proportion"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )







```




```{r, CR-UNSC_Citations_Network_blackwhite, fig.width = 20, fig.height = 20,  dev = "png", fig.cap = "The citation network of the UNSC"}



g <- igraph_citations
ggraph(g, "stress", niter = 4000, bbox = 25) + 
    geom_edge_diagonal(colour = "black", edge_width = 0.1)+
    geom_node_point(size = 0.1,
                    color = "black")+
    theme_void()+
    labs(
        title = paste(prefix.figuretitle,
                      "| The complete UNSC citation network"),
        caption = caption
    )+
    theme(
        plot.title = element_text(size = 14,
                                  face = "bold",
                                  color = "black"),                        
        plot.background = element_rect(fill = "white"),
        plot.caption = element_text(color = "black"),
        plot.margin = margin(10, 20, 10, 10)
    )
    


```




\newpage
# Linguistic Metrics


## Explanation of Metrics

We provide a number of classic linguistic metrics and visualize their distributions to better communicate the scope of the corpus and its constituent documents:


\medskip

\begin{centering}
\begin{longtable}{P{3.5cm}p{10.5cm}}

\toprule

Metric & Definition\\

\midrule

Characters & Characters roughly correspond to graphemes, the smallest functional unit in a writing system. The word \enquote{judge} is composed of 5 characters, for example.\\
Tokens & An arbitrary character sequence delimited by whitespace on both sides, e.g. it roughly corresponds to the notion of a \enquote{word}. However, due to its strictly syntactical definition it might also include arbitrary sequences of numbers or special characters.\\
Types & Unique tokens. If, for example, the token \enquote{human} appeared one hundred times in a given document, it would be counted as only one type. \\
Sentences & Corresponds approximately to the colloquial definition of a sentence. The exact rules for determining sentence boundaries are very complex and may be reviewed in \enquote{Unicode Standard: Annex No 29}.\\

\bottomrule

\end{longtable}
\end{centering}





## Summary Statistics


\ra{1.3}
```{r}



kable(lingstats.summary,
      digits = 2,
      format.args = list(big.mark = ","),
      format = "latex",
      booktabs = TRUE,
      longtable = TRUE)


```



## Distributions of Document Length

The diagrams in this section are combined violin and box plots. They are especially useful in visualizing distributions of quantitative variables. Their interpretation is fairly straightforward: the greater the area under the curve for a given range, the more frequent the values are in this range. The thick center line of the box indicates the median, the outer lines of the box the first and third quartiles. Whiskers extend outwards to 1.5 times the inter-quartile range (IQR). Outliers beyond 1.5 times IQR are shown as individual points.

Please note that the x-axis is logarithmically scaled, i.e. in powers of 10. It therefore increases in a non-linear fashion. Additional sub-markings are included to assist with interpretation.



```{r, CR-UNSC_Distributions_LinguisticMetrics, fig.height = 10, fig.width = 8.3}
## When plotting a boxplot on a logarithmic scale the standard geom_boxplot() function from ggplot2 incorrectly performs the statistical transformation first before calculating the boxplot statistics. While median and quartiles are based on ordinal position the inter-quartile range differs depending on when statistical transformation is performed.

## Solutions are based on this SO question: https://stackoverflow.com/questions/38753628/ggplot-boxplot-length-of-whiskers-with-logarithmic-axis


dt.allmetrics.en <- melt(var_lingstats,
                         measure.vars = rev(c("nchars",
                                              "ntokens",
                                              "ntypes",
                                              "nsentences")))

ggplot(dt.allmetrics.en, aes(x = value,
                             y = variable))+
    geom_violin()+
    stat_summary(fun.data = f.boxplot.body,
                 geom = "errorbar",
                 width = 0.1) +
    stat_summary(fun.data = f.boxplot.body,
                 geom = "boxplot",
                 width = 0.1) +
    stat_summary(fun.data = f.boxplot.outliers,
                 geom = "point",
                 size =  0.5,
                 alpha = 0.1)+
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
    annotation_logticks(sides = "b")+
    coord_cartesian(xlim = c(1, 10^6))+
    scale_y_discrete(labels = rev(c("Characters",
                                    "Tokens",
                                    "Types",
                                    "Sentences")))+
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Distributions of Document Length (EN)"),
        caption = caption,
        x = "Value",
        y = "Linguistic Metric"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )

        

```



# Metadata Frequency Tables
 
\ra{1.3}
 

## By Year


```{r, CR-UNSC_Barplot_Resolutions-by-Year, fig.height = 6, fig.width = 9}
freqtable <- f.fast.freqtable(dt.final,
                                 varlist = "year",
                                 sumrow = TRUE,
                                 output.list = TRUE,
                                 output.kable = FALSE,
                                 output.csv = FALSE,
                                 align = c("p{5cm}"))[[1]]

freqtable.nosum <- freqtable[-.N][,lapply(.SD, as.numeric)]





ggplot(data = freqtable.nosum) +
    geom_bar(aes(x = year,
                 y = N),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Resolutions by Year"),
        caption = caption,
        x = "Year of Adoption",
        y = "Resolutions"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )

```


\vspace{0.5cm}


```{r}

kable(freqtable,
      format = "latex",
      align = 'P{3cm}',
      booktabs = TRUE,
      longtable = TRUE,
      col.names = c("Year",
                    "Resolutions",
                    "% Total",
                    "% Cumulative"))  %>% kable_styling(latex_options = "repeat_header")

```




## By Country Mentioned


```{r, CR-UNSC_Barplot_Resolutions-by-Country, fig.height = 14, fig.width = 10}
split <- unlist(stringi::stri_split(dt.final$iso_name, regex = "\\|"))
country <- split[split != ""]


freqtable <- f.fast.freqtable(data.table(country),
                              sumrow = TRUE,
                              output.list = TRUE,
                              output.kable = FALSE,
                              output.csv = FALSE,
                              align = c("p{5cm}"))[[1]]



freqtable.nosum <- freqtable[-.N][order(-N)][1:50]





ggplot(data = freqtable.nosum) +
    geom_bar(aes(x = reorder(country,
                             N),
                 y = N),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    coord_flip()+
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Top 50 Countries mentioned"),
        caption = caption,
        x = "Country",
        y = "Resolutions"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )

```



\vspace{0.5cm}


```{r}

kable(freqtable,
      format = "latex",
      align = 'P{3cm}',
      booktabs = TRUE,
      longtable = TRUE,
      col.names = c("Country",
                    "Resolutions",
                    "% Total",
                    "% Cumulative"))  %>% kable_styling(latex_options = "repeat_header")

```



\newpage
## By Region of Countries Mentioned


```{r, CR-UNSC_Barplot_Resolutions-by-Region, fig.height = 6, fig.width = 9}
split <- unlist(stringi::stri_split(dt.final$m49_region, regex = "\\|"))
region <- split[split != ""]


freqtable <- f.fast.freqtable(data.table(region),
                              sumrow = TRUE,
                              output.list = TRUE,
                              output.kable = FALSE,
                              output.csv = FALSE,
                              align = c("p{5cm}"))[[1]]



freqtable.nosum <- freqtable[-.N][order(-N)]





ggplot(data = freqtable.nosum) +
    geom_bar(aes(x = reorder(region,
                             N),
                 y = N),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    coord_flip()+
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Top Regions of Countries Mentioned"),
        caption = caption,
        x = "Region",
        y = "Resolutions"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )

```



\vspace{0.5cm}


```{r}

kable(freqtable,
      format = "latex",
      align = 'P{3cm}',
      booktabs = TRUE,
      longtable = TRUE,
      col.names = c("Region",
                    "Resolutions",
                    "% Total",
                    "% Cumulative"))  %>% kable_styling(latex_options = "repeat_header")

```



\newpage
## By Sub-Region of Countries Mentioned


```{r, CR-UNSC_Barplot_Resolutions-by-SubRegion, fig.height = 6, fig.width = 9}
split <- unlist(stringi::stri_split(dt.final$m49_region_sub, regex = "\\|"))
subregion <- split[split != ""]


freqtable <- f.fast.freqtable(data.table(subregion),
                              sumrow = TRUE,
                              output.list = TRUE,
                              output.kable = FALSE,
                              output.csv = FALSE,
                              align = c("p{5cm}"))[[1]]



freqtable.nosum <- freqtable[-.N][order(-N)]





ggplot(data = freqtable.nosum) +
    geom_bar(aes(x = reorder(subregion,
                             N),
                 y = N),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    coord_flip()+
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Top Sub-Regions Mentioned"),
        caption = caption,
        x = "Sub-Region",
        y = "Resolutions"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )

```



\vspace{0.5cm}


```{r}

kable(freqtable,
      format = "latex",
      align = 'P{3cm}',
      booktabs = TRUE,
      longtable = TRUE,
      col.names = c("Sub-Region",
                    "Resolutions",
                    "% Total",
                    "% Cumulative"))  %>% kable_styling(latex_options = "repeat_header")

```







\newpage
## By Subject



```{r, CR-UNSC_Barplot_Resolutions-by-Subject, fig.height = 14, fig.width = 10}
split <- unlist(stringi::stri_split(dt.final$subjects, regex = "\\|"))
subjects <- split[split != ""]


freqtable <- f.fast.freqtable(data.table(subjects),
                              sumrow = TRUE,
                              output.list = TRUE,
                              output.kable = FALSE,
                              output.csv = FALSE,
                              align = c("p{5cm}"))[[1]]

freqtable$subjects <- tools::toTitleCase(tolower(freqtable$subjects))

freqtable$subjects <- gsub("Un", "UN", freqtable$subjects)
freqtable$subjects <- gsub("Vii", "VII", freqtable$subjects)

freqtable.nosum <- freqtable[-.N][order(-N)][1:50]





ggplot(data = freqtable.nosum) +
    geom_bar(aes(x = reorder(subjects,
                             N),
                 y = N),
             stat = "identity",
             fill = "black",
             color = "black",
             width = 0.5) +
    coord_flip()+
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| 50 Most Frequent Subjects"),
        caption = caption,
        x = "Subject",
        y = "Resolutions"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )

```


```{r}

kable(freqtable.nosum,
      format = "latex",
      align = 'P{3cm}',
      booktabs = TRUE,
      longtable = TRUE,
      col.names = c("Subject",
                    "Resolutions",
                    "% Total",
                    "% Cumulative"))  %>% kable_styling(latex_options = "repeat_header")

```


\newpage
## Proportions of Votes Cast


```{r, CR-UNSC_Distributions_Voting, fig.height = 10, fig.width = 10}

## Normalize by Total

dt.vote <- dt.final[,.(vote_yes, vote_no, vote_abstention, vote_nonvote, vote_total)]
dt.vote <- dt.vote / dt.vote$vote_total
dt.vote$vote_total <- NULL

names <- names(dt.vote)

dt.allmetrics <- melt(dt.vote,
                      measure.vars = rev(names))

# Plot
ggplot(dt.allmetrics) +
    geom_bar(aes(x = value),
             fill = "black",
             color = "black",
             width = 0.01)+
    facet_wrap(~variable)+
    theme_bw() +
    labs(
        title = paste(prefix.figuretitle,
                      "| Voting Data"),
        caption = caption,
        x = "Proportion of Votes Cast",
        y = "Resolutions"
    )+
    theme(
        text = element_text(size = 14),
        plot.title = element_text(size = 14,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(10, 20, 10, 10)
    )





```




```{r}

freqtable.nosum <- dt.allmetrics[,.N,keyby =c("variable", "value")]

kable(freqtable.nosum,
      format = "latex",
      align = 'P{3cm}',
      booktabs = TRUE,
      longtable = TRUE,
      col.names = c("Variable",
                    "Proportion",
                    "N"))  %>% kable_styling(latex_options = "repeat_header")

```





# FAIR Data Conformity Declaration

The FAIR Principles lay out an influential set of guiding standards for the management of scientific data. Four principles define the FAIR standard: [F]indability, [A]ccessibility [I]nteroperability and [R]eusability. 

It is the intention of the author(s) to be fully compliant with the FAIR standard. This conformity declaration is intended to provide further information on what measures have been taken to achieve this compliance.

For the original publication proposing the FAIR standard, please see: Wilkinson, M. D. et al. The FAIR Guiding Principles for scientific data management and stewardship. Sci. Data 3:160018 doi: 10.1038/sdata.2016.18 (2016).


## [F] Findable

**[F1] (Meta)data are assigned a globally unique and persistent identifier**

- The dataset and source code are published with Zenodo, a major scientific repository operated by CERN.
- Zenodo issues a DOI for the dataset as a whole and a DOI for each individual version of the dataset and source code.

\medskip

**[F2] Data are described with rich metadata (defined by R1 below)**

- Zenodo's metadata is compliant with DataCite's Metadata Schema minimum and recommended terms
- The author(s) have provided significant metadata to augment the Zenodo record, such as a lengthy description, keywords, publication details, license, related works and contact details for the maintainer(s)

\medskip


**[F3] Metadata clearly and explicitly include the identifier of the data they describe**

- Zenodo requires the DOI as a top-level and mandatory field in the metadata of each record

\medskip

**[F4] (Meta)data are registered or indexed in a searchable resource**

- Metadata is indexed in and searchable via Zenodo
- Metadata is indexed in and searchable via DataCite



## [A] Accessible

**[A1] (Meta)data are retrievable by their identifier using a standardised communications protocol**

- Zenodo provides a public OAI-PMH interface to retrieve metadata of individual records and whole collections
- Zenodo provides a public REST API to retrieve metadata of individual records

\medskip

**[A1.1] The protocol is open, free, and universally implementable**

- The OAI-PMH and REST APIs provided by Zenodo are based on open, free and universally implementable protocols 

\medskip

**[A1.2] The protocol allows for an authentication and authorisation procedure, where necessary**

- Zenodo provides all metadata publicly and without authentication under a public domain license

\medskip

**[A2] Metadata are accessible, even when the data are no longer available**

- Zenodo guarantees that metadata remain available for the lifetime of the parent organization CERN, which has a defined experimental program for the next 20 years
- Metadata are stored in different servers than the data at Zenodo
- Zenodo commits to providing a "data tombstone" of the record that contains all metadata even if data becomes unavailable for legal or other reasons




## [I] Interoperable

**[I1] (Meta)data use a formal, accessible, shared, and broadly applicable language for knowledge representation**

- Zenodo metadata is internally stored as JSON and can be exported to MARCXML, Dublin Core XML, CSL, DataCite JSON, DataCite XML, BibTeX, GeoJSON and DCAT

\medskip

**[I2] (Meta)data use vocabularies that follow FAIR principles**

- Zenodo refers to external vocabularies for license (Open Definition), funders (FundRef) and grants (OpenAIRE)

\medskip

**[I3] (Meta)data include qualified references to other (meta)data**

- The CR-UNSC embeds the Concept DOI and Version DOI for the relevant Zenodo record in the CSV dataset and the Codebook
- The CR-UNSC includes the unique URL for the resolution text in all six UN languages, the URL for the draft and meeting record in English and the URL for the UN Digital Library record pages of the resolution, draft and meeting record. UN Digital Library record pages provide machine-readable metadata in a wide range of export formats.




## [R] Reusable

**[R1] (Meta)data are richly described with a plurality of accurate and relevant attributes**


**[R1.1] (Meta)data are released with a clear and accessible data usage license**

- Zenodo metadata includes standardized representations of each license compliant with the OpenDefinition standard
- The CR-UNSC data is published under a standardized Creative Commons CC0 1.0 waiver
- The CR-UNSC source code is published under a standardized GNU GPL v3 license
- The CR-UNSC embeds the  data license in the CSV file and in the Codebook

\medskip

**[R1.2] (Meta)data are associated with detailed provenance**

- The CR-UNSC embeds the Concept DOI and Version DOI for the relevant Zenodo record in the CSV dataset and the Codebook
- The CR-UNSC includes the unique URL for the resolution text in all six UN languages, the URL for the draft and meeting record in English and the URL for the UN Digital Library record pages of the resolution, draft and meeting record

\medskip

**[R1.3] (Meta)data meet domain-relevant community standards**

- The CR-UNSC was crafted by specialized international lawyers, complies with international law terminology and respects international legal usage wherever possible
- The CR-UNSC respects United Nations terminology and United Nations document symbols
- The CR-UNSC adapts all metadata conventions from the UN Digital Library
- The CR-UNSC complies with ISO and UN M49 standards for country and area codes




\newpage
# Cryptographic Signatures


## Two Phase Signature


The integrity and veracity of the ZIP archives and other output of the data set are guaranteed with two-phase *hash-and-sign* signature process.

In **Phase I** the data pipeline automatically computes digital fingerprints (hashes) with two different secure algorithms (SHA2-256 und SHA3-512) and stores these in a CSV file.

In **Phase II** the CSV files with hashes is manually signed with a secret GPG key.

This process ensures that the compilation of the data set can be performed by anyone, such as in scientific replication studies, but provides the same guarantees as signing the full data set would. 



## Personal GPG Key

The CSV file is signed with the personal GPG key of the first author. The public key is included with the data set and source code publication on Zenodo, as well as the project GitHub repository. The key is identified as follows:
 
 **Name:** Sean Fobbe (fobbe-data@posteo.de)
 
 **Fingerprint:** FE6F B888 F0E5 656C 1D25  3B9A 50C4 1384 F44A 4E42





\newpage






```{r, results = "asis"}
cat(readLines(tar_read(changelog)),
    sep = "\n")

```






# Replication Parameters


```{r}
system2("openssl", "version", stdout = TRUE)

sessionInfo()

```


# Bibliography
