---
title: "Robustness Checks | Corpus of Resolutions: UN Security Council"
author: "Seán Fobbe, Niccolò Ridi and Lorenzo Gasbarri"
geometry: margin=3cm
papersize: a4
fontsize: 11pt
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    pandoc_args: --listings
    includes:
      in_header: ../tex/Preamble_EN.tex
      before_body: [../temp/Definitions.tex,../tex/Titlepage_Robustness.tex]
bibliography: ../temp/packages.bib
nocite: '@*'
---



```{r, setup, include=FALSE}
knitr::opts_chunk$set(fig.path = file.path("..", "analysis/"),
                      dev = config$fig$format,
                      dpi = config$fig$dpi,
                      fig.align = config$fig$align,
                      echo = TRUE,
                      warning = TRUE,
                      message = TRUE)

```


# Overview

## Load results

```{r}
tar_load(latexdefs)
tar_load(dt.var_codebook)
tar_load(lingstats.summary)
tar_load(dt.record.final)
tar_load(dt.download.final)
tar_load(pdf_res_ar)
tar_load(pdf_res_en)
tar_load(pdf_res_es)
tar_load(pdf_res_fr)
tar_load(pdf_res_ru)
tar_load(pdf_res_zh)
tar_load(dt.final)
tar_load(langtest)
tar_load(ocrtest)
tar_load(igraph_citations)

```

## Count Automated Tests


```{r}

Rfiles <- list.files("functions", pattern = "\\.R$", full.names = TRUE)
code <- unlist(lapply(Rfiles, readLines))


```


### Tests


```{r}

sum(stringi::stri_count(regex = "test_that\\(", code))

```

### Expectations

```{r}

sum(stringi::stri_count(regex = "expect_", code))

```



# Introduction

Lorem Ipsum. test




# Visualize Pipeline



```{r, CR-UNSC_00_Pipeline_Graph_blue, fig.width = 16, fig.height = 18, fig.pos = "p", fig.cap = "The complete data set compilation process."}


edgelist <- tar_network(targets_only = TRUE)$edges
setDT(edgelist)

g  <- igraph::graph.data.frame(edgelist,
                               directed = TRUE)

ggraph(g,
       'sugiyama') + 
    geom_edge_diagonal(colour = "#55c8ff")+
    geom_node_point(size = 2,
                    color = "white")+
    geom_node_text(aes(label = name),
                   color = "white",
                   size = 2,
                   repel = TRUE)+
    theme_void()+
    labs(
        title = paste(prefix.figuretitle,
                      "| Complete data set compilation process"),
        caption = caption
    )+
    theme(
        plot.title = element_text(size = 14,
                                  face = "bold",
                                  color = "white"),                        
        plot.background = element_rect(fill = "black"),
        plot.caption = element_text(color = "white"),
        plot.margin = margin(10, 20, 10, 10)
    )

```



# Completeness of Download


## Download: Missing PDF Files

```{r}

setdiff(paste0(dt.download.final[!is.na(url_res_ar)]$doc_id, "_AR.pdf"), basename(pdf_res_ar))
setdiff(paste0(dt.download.final[!is.na(url_res_ar)]$doc_id, "_EN.pdf"), basename(pdf_res_en))
setdiff(paste0(dt.download.final[!is.na(url_res_ar)]$doc_id, "_ES.pdf"), basename(pdf_res_es))
setdiff(paste0(dt.download.final[!is.na(url_res_ar)]$doc_id, "_FR.pdf"), basename(pdf_res_fr))
setdiff(paste0(dt.download.final[!is.na(url_res_ar)]$doc_id, "_RU.pdf"), basename(pdf_res_ru))
setdiff(paste0(dt.download.final[!is.na(url_res_ar)]$doc_id, "_ZH.pdf"), basename(pdf_res_zh))

```



# Missing Values



```{r, results = "asis"}

missingvalues <- f.missingvalues(x = dt.final,
                                 kable = TRUE,
                                 dir.out = dir.analysis,
                                 prefix.files = prefix.files)


```



f.token.processor <- function(corpus){
    tokens <- tokens(corpus,
                     remove_numbers = TRUE,
                     remove_punct = TRUE,
                     remove_symbols = TRUE,
                     remove_separators = TRUE)
    tokens <- tokens_tolower(tokens)
    tokens <- tokens_remove(tokens,
                            pattern = c(stopwords("english"),
                                        stopwords("french"),
                                        stopwords("spanish")))
    return(tokens)
}


# Text Quality Comparison

To compare the text quality of extracted, OCR and gold (expert revised) variants we calculate the number of features (unique tokens) for each language and process following a standard pre-processing workflow. During pre-processing we remove numbers, punctuation, symbols and separators, lowercase all tokens and remove stopwords in English, French and Spanish.

The resulting number of features determines the quality and speed with which document-feature matrix (or document-term matrix) oriented workflows can proceed. Lower is better.


```{r}

print(ocrtest)

```





# Documents with Low Character Count


## Arabic

```{r}
dt.final[nchar(dt.final$text_ar) < 200, .(doc_id, text_ar)]

```


## English

```{r}
dt.final[nchar(dt.final$text) < 200, .(doc_id, text)]

```

## Spanish

```{r}
dt.final[nchar(dt.final$text_es) < 200, .(doc_id, text_es)]

```


## French

```{r}
dt.final[nchar(dt.final$text_fr) < 200, .(doc_id, text_fr)]

```


## Russian

```{r}
dt.final[nchar(dt.final$text_ru) < 200, .(doc_id, text_ru)]

```


## Chinese

```{r}
dt.final[nchar(dt.final$text_zh) < 200, .N]

```







# Frequency Tables


## Selected Variables

 **Note:** Frequency tables are calculate only for these variables.

```{r}
varnames <- dt.var_codebook[freqtable == 1]$varname
varnames <- gsub("\\\\", "", varnames)
print(varnames)


```




```{r}

## Define prefix

prefix <- paste0(config$project$shortname,
                 "_01_FrequencyTable_var-")

```

## Run Frequency Tables


```{r, results = "asis"}

f.fast.freqtable(dt.final,
                 varlist = varnames,
                 sumrow = TRUE,
                 output.list = FALSE,
                 output.kable = TRUE,
                 output.csv = TRUE,
                 outputdir = dir.analysis,
                 prefix = prefix,
                 align = c("p{5cm}",
                           rep("r", 4)))

```











```{r, results = "asis"}
cat(readLines(tar_read(changelog)),
    sep = "\n")

```






# Replication Parameters


```{r}
system2("openssl", "version", stdout = TRUE)

sessionInfo()

```


# Bibliography
